Bayesian model comparison for rare variant association studies of multiple phenotypes

### 2017-12-23 tex/MVMetaLearnMRP2017OctoberMRPMM.tex
Minor text update

@@

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{/Users/mrivas/Dropbox/MultiplePhenotypesManuscript/hdf5MAMBAMRP.pdf}
  \caption{Our HDF5 implementation contained the following components: first, a group with one table per annotation file. All effect size (beta) values and study-specific annotations were contained here, and the number of tables is limited by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Second, a group with site-site covariance data. While these covariance matrices may have dimension $M\ \textrm{(the number of variants)} \times M$, we store the data as tables, each row specifiying the covariance between two variants. The number of tables should be the same as the previous set, capped by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Third, we store one table with sigma values for each study/phenotype combination. In the event that the traits were rank-normal transformation was performed these sigma values are equal to 1. These are used to compute correlation between two datasets. Finally, we store a matrix/table pair for Vy null and its index. The Vy null matrix has dimensions $ (S \times K) \times (S \times K)$ each entry specifying the estimated correlation of effect sizes between two datasets. The index table encodes row/column position of each dataset.}
  \label{hdf5}
\end{figure}

>>>>

\subsubsection{UK Biobank Asthma Application}
For the Manhattan plots \ref{Fig3} and table \ref{Tab1}, we removed any genes with non-unique gene symbols. We also removed the sense overlapping gene \textit{CTD-3064M3.3} and and the antisense gene \textit{ZFAT-AS1} since these genes overlap \textit{GPR20} and \textit{ZFAT} respectively and therefore have the same $\log_{10}$ Bayes Factors as those genes.

@@

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/hdf5MAMBAMRP.pdf}
  \caption{Our HDF5 implementation contained the following components: first, a group with one table per annotation file. All effect size (beta) values and study-specific annotations were contained here, and the number of tables is limited by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Second, a group with site-site covariance data. While these covariance matrices may have dimension $M\ \textrm{(the number of variants)} \times M$, we store the data as tables, each row specifiying the covariance between two variants. The number of tables should be the same as the previous set, capped by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Third, we store one table with sigma values for each study/phenotype combination. In the event that the traits were rank-normal transformation was performed these sigma values are equal to 1. These are used to compute correlation between two datasets. Finally, we store a matrix/table pair for Vy null and its index. The Vy null matrix has dimensions $ (S \times K) \times (S \times K)$ each entry specifying the estimated correlation of effect sizes between two datasets. The index table encodes row/column position of each dataset.}
  \label{hdf5}
\end{figure}
